---
title: "covid 19"
author: "Adriana Pimentel"
date: "10/5/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex




Table of patients:
```{r}

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

## We create two bar charts - one based on frequency and the other on percent, use ggplot commands to do this

`

```{r}
barchartGC(~result + sex,data=kRdata)
```

In this data there are more women than men alive. They outnumber the males significantly as shown by the blue bar in the frequency chart above. The chart also shows that in this group people there are more people alive than dead as shown by the two bars labeled alive on the left and the two bars labeled dead on the right. 

```{r}
barchartGC(~result + sex,data=kRdata, type="percent")

``` 





  
## Numerical results


## Inferential results 




## Conclusions

